Dataset Summary

### 2018-08-03 Cleaning & subset.Rmd
Add strain into body size data; summary stats by population

```{r}
data <- data_raw %>% 
  mutate(parameter_name = tolower(parameter_name) ) %>%
  filter(age_in_days > 0 & age_in_days < 500) %>% 
  select(production_center, project_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
  arrange(production_center, biological_sample_id, age_in_days)
```

@@

>>>>

```{r}
data <- data_raw %>% 
  mutate(parameter_name = tolower(parameter_name) ) %>%
  filter(age_in_days > 0 & age_in_days < 500) %>% 
  select(production_center, strain_name, experiment_id, external_sample_id, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
  arrange(production_center, biological_sample_id, age_in_days)
```

@@

# For variance analysis

- population has > 5 individuals

keep age closet t0 10 
```{r}

data %>% 
  filter(
    age_in_days >= 98, 
    parameter_name == "body weight") %>%
  mutate(age_diff=abs(100-age_in_days)) %>%
  group_by(biological_sample_id) %>%
  filter(age_diff == min(age_diff)) %>%
  mutate(population = sprintf("%s-%s-%s", strain_name, production_center, sex) )  -> x

i <- match(unique(x$biological_sample_id), x$biological_sample_id)

data2 <- x[i,] 
```

Calculate number of reocrds per population
```{r}
data2 %>% 
  group_by(population) %>%
  summarise(
    n_records = n_distinct(biological_sample_id)
  ) -> population_size
hist(population_size$n_records)

sum(population_size$n_records < 10)
```

```{r}

data %>% 
  filter(
    age_in_days >= 100, 
    parameter_name == "body weight") %>%
  select(biological_sample_id, external_sample_id) %>%
  arrange(external_sample_id) %>%
  data.frame()

data %>% 
  filter(
    age_in_days >= 100, 
    parameter_name == "body weight") %>%
  mutate(age_diff=abs(100-age_in_days)) %>%
  group_by(biological_sample_id) %>%
  filter(age_diff == min(age_diff)) -> x

i <- match(unique(x$biological_sample_id), x$biological_sample_id)

x[i,] -> x

# check only one record per individual

table(x$biological_sample_id) -> z 
z[z!=1]

```

### 2018-08-03 Overview.Rmd
Add strain into body size data; summary stats by population

```{r}
select(filter(data, biological_sample_id == "107609"), sex, production_center, project_name, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
```

>>>>

```{r}
select(filter(data_raw, biological_sample_id == "107609"), sex, production_center, external_sample_id, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
```
